A meta-analysis of the impacts of best management practices on nonpoint source pollutant concentration.

### 2024-03-07 frontiers_submission/frontiers_submission.Rmd
prep for submission

In summary, we used multi-level random effects meta-regression models to estimate overall BMP effectiveness from systematically reviewed studies. 
Although there was relatively high variance between studies, we found strong evidence that BMPs reduce overall mean FIB, TN, TP, and TSS concentrations.
Influent concentrations moderated BMP efficiency for both FIB and PO~4~, with larger removal rates at high influent concentrations.
We found that aridity and BMP subcategory moderated BMP performance for only FIB.
Most likely, site specific design and climate variables not captured in our review or by our choice in BMP classification approach play a more important role in explaining BMP performance variability.
Future efforts should seek to retrieve more detailed study information.
Furthermore, our systematic review highlights the poor spatial coverage of BMP studies. 
The reviewed studies therefore fail to incorporate the range of soil, climate, and runoff conditions needed to adequately link BMP performance to local predictors.

@@

@@

Supplementary Material should be uploaded separately on submission, if there are
Supplementary Figures, please include the caption in the same file as the
figure. LaTeX Supplementary Material templates can be found in the Frontiers
LaTeX folder

>>>>

@@

In summary, we used multi-level random effects meta-regression models to estimate overall BMP effectiveness from systematically reviewed studies. 
Although there was relatively high variance between studies, we found strong evidence that BMPs reduce overall mean FIB, TN, TP, and TSS concentrations.
Influent concentrations moderated BMP efficiency for both FIB and PO~4~, with larger removal rates at high influent concentrations.
We found that aridity and BMP subcategory moderated BMP performance for only FIB.
Most likely, site specific design and climate variables not captured in our review or by our choice in BMP classification approach play a more important role in explaining BMP performance variability.
Future efforts should seek to retrieve more detailed study information.
Furthermore, our systematic review highlights the poor spatial coverage of BMP studies. 
The reviewed studies therefore fail to incorporate the range of soil, climate, and runoff conditions needed to adequately link BMP performance to local predictors.
To adequately estimate the effects of moderating variable on BMP performance we suggest that there is a need for additional aligned BMP studies across regions and conditions.

@@

Supplementary Material for this article has been uploaded with the submission.
